---
title: "Homework #5"
author: "Diana Ballesteros Gonzalez"
date: "11/7/2018"
output: github_document
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
set.seed(1)

knitr::opts_chunk$set(
  fig.width = 10,
  fig.asp = 1.0,
  out.width = "90%"
)

theme_set(theme_bw() + theme(legend.position = "bottom"))
```

*Problem 1*
This zip file contains data from a longitudinal study that included a control arm and an experimental arm. Data for each participant is included in a separate file, and file names include the subject ID and arm.

Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time:


Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary
Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.
```{r problem_1, include = FALSE}

## Using functions and mapping to pull in data from different files 
list_path = list.files(path = "./data", full.names = TRUE) 
remove_path = basename(list_path)
  
files_function = 
  function(data, name){
  list(read_csv(data) %>% 
  mutate(id = name))
}

path_names = 
  map2(list_path, remove_path, files_function)

problem_1_df = 
  map_df(path_names, bind_rows)
```

```{r}
#Tidying the data
tidy_problem_1_df = 
problem_1_df %>% 
  gather(key = "week", value = "score", week_1:week_8) %>% 
  mutate(week = as.numeric(str_extract(week, "\\d"))) %>% 
  separate(id, into = c("arm","id"), sep = "_") %>% 
  mutate(id = str_replace(id, ".csv", ""),
         arm = str_replace(arm, "con", "control"), 
         arm = str_replace(arm, "exp", "experimental")) 
```

Make a spaghetti plot: 
Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.

```{r}
tidy_problem_1_df %>% 
  ggplot(aes(x = week, y = score)) + 
  geom_line() + 
  facet_grid(~arm) + 
  labs(
    title = "Average Max Temperature in January and July in Each Station Across Years",
    x = "Year",
    y = "Average Max Temperature",
    caption = "Data from the nyoaa dataset"
  ) + 
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) 
```

