---
title: "Homework #5"
author: "Diana Ballesteros Gonzalez"
date: "11/7/2018"
output: github_document
---

```{r setup}
library(tidyverse)
library(rvest)

set.seed(1)

knitr::opts_chunk$set(
  fig.width = 10,
  fig.asp = 1.0,
  out.width = "90%"
)

theme_set(theme_bw() + theme(legend.position = "bottom"))
```

###**Problem 1**
```{r problem_1, include = FALSE}

## Using functions and mapping to pull in data from different files 
list_path = list.files(path = "./data", full.names = TRUE) 
remove_path = basename(list_path)
  
files_function = 
  function(data, name){
  list(read_csv(data) %>% 
  mutate(id = name))
}

path_names = 
  map2(list_path, remove_path, files_function)

problem_1_df = 
  map_df(path_names, bind_rows)
```

```{r}
#Tidying the data
tidy_problem_1_df = 
problem_1_df %>% 
  gather(key = "week", value = "score", week_1:week_8) %>% 
  mutate(week = as.numeric(str_extract(week, "\\d"))) %>% 
  separate(id, into = c("arm","id"), sep = "_") %>% 
  mutate(id = str_replace(id, ".csv", ""),
         arm = str_replace(arm, "con", "control"), 
         arm = str_replace(arm, "exp", "experimental")) 
```

Creating a spaghetti plot: 
```{r}
tidy_problem_1_df %>% 
  group_by(id) %>% 
  ggplot(aes(x = week, y = score, color = id)) + 
  geom_line() + geom_point() + 
  facet_grid(~arm) + 
  labs(
    title = "Spaghetti plot showing observations over times",
    x = "Week",
    y = "Observation"
  ) + 
  viridis::scale_color_viridis(
    name = "ID", 
    discrete = TRUE) + 
  theme_bw()
```

Comment on differences between groups: 

* In the control group, the trend seems to remain at the same levels meanwhile the experimental groups shows observations increasing. Additionally, the experimental groups seems to have higher observation by week 8 in comparison to week 8 in the control group. Overall, the observations in the experimental group seem to be higher in comparison to the control group. 

###**Problem 2**

Describe the raw data: 

```{r}
## Import data 
homicide_data = 
  read_csv("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv") %>% 
  janitor::clean_names() %>% 
  mutate(city_state = paste(city, state, sep = ", "))
```

Total number of homicides
```{r}
total_num_homicides_df = 
homicide_data %>% 
  group_by(city_state) %>% 
  summarize(total_num_homicides = n()) 
```

Number of unsolved homicides
```{r}
num_unsolved_homicides_df = 
homicide_data %>% 
  filter(disposition == "Closed without arrest" | disposition == "Open/No arrest") %>% 
  group_by(city_state) %>% 
  summarize(num_unsolved_homicides = n()) 
```

```{r}
all_df = 
  left_join(num_unsolved_homicides_df, total_num_homicides_df, by = "city_state")
```

```{r}
prop_function = function(x,y) {
    prop.test(x = x,n = y) %>% 
    broom::tidy() %>% 
    select(estimate, conf.low, conf.high)
}

homicides_total = 
  map2(.x = all_df$num_unsolved_homicides, 
       .y = all_df$total_num_homicides,
       ~prop_function(.x, .y)) %>% 
  bind_rows() %>% 
  bind_cols(all_df) %>% 
  janitor::clean_names() %>% 
  select(city_state, num_unsolved_homicides, total_num_homicides, estimate, conf_low, conf_high)
```

Making a plot for the propotion of homicides

```{r}
homicides_total %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate, color = city_state)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = conf_low, ymax = conf_high)) + 
  labs(
    title = "Proportion of unsolved homicide cases throughout 50 major US cities",
    x = "City Name",
    y = "Proportion of unsolved homicide cases"
  ) + 
  theme(legend.position = "none") + 
  theme(axis.text.x = element_text(angle = 90, size = 7))
```
